---
title: "Cabbages"
author: "Emann Malik"
date: "February 13, 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The box plot shows that cultivation method c52 contains higher Vitamin C levels than cultivation method c39. The median amount of Vitamin C c52 has is about 64 while the median amount c39 has is only about 51.
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
favstats(VitC~Cult,data=veggy)
```
  
The table shows that the average amount of Vitamin C in cultivation method c52 is 64.4 and the average amount of Vitamin C in cultivation method c39 is 51.5. The standard deviation for c52 is about 8.46, meaning the observations are, on average, that amount of Vitamin C content away from that of the mean observation. For c39 the standard deviation is about 7.12, meaning the observations here are closer to the mean than the ones in c52 are.  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(VitC~Cult,data=veggy)
```
  
The null hypothesis states that there is no difference between the average Vitamin C level of cultivation methods c39 and c52. The alternative hypothesis states that the average Vitamin C level of cultivation method c39 is statistically different than that of c52. The p-value, 0.00000003405, is a very small number. This value represents the chance of getting the results just given if the null hypothesis is true. So, we reject the null hypothesis in favor of the alternative; there is a statistically different average level of Vitamin C between cultivation methods c39 and c52. c52 has the higher levels and is therefore the better method. The t-statistic further solidifies this conclusion since it is about -6.39. The further away this value is from 0, the bigger the difference is between our results and the null hypothesis.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
In conclusion, cultivation method c52 produces a higher content of Vitamin C than c39 does.
  